---
title: "affective-anovas"
author: "Paige Tuttosi"
date: '2022-04-04'
output: html_document
---


##########################################################
Here we look at which features are signifigantly different between agression levels by Segment
and parent label for all dat as well as only noisy and only non-noisy
##########################################################

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(AICcmodavg)
```

## Setup Data

Load data

```{r}
data <- read.csv("./extracted/preprocessed_data_full.csv", header = TRUE, colClasses = c("numeric", "numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric", "factor", "factor", "factor"))
```

```{r}
summary(data)
```


## Parent Label Anova- All Data

```{r}
energy_anova_parent <- aov( get_energy ~ parent_label, data = data)

summary(energy_anova_parent)
```

```{r}
harmonics_anova_parent <- aov(analyse_harmonics ~ parent_label , data = data)

summary(harmonics_anova_parent)
```
```{r}
max_intensity_anova_parent <- aov(get_max_intensity ~ parent_label , data = data)

summary(max_intensity_anova_parent)
```

```{r}
intensity_anova_parent <- aov(analyse_intensity ~ parent_label , data = data)

summary(intensity_anova_parent)
```

```{r}
pitch_anova_parent <- aov(analyse_pitch ~ parent_label , data = data)

summary(pitch_anova_parent)
```


```{r}
pitch_range_anova_parent <- aov(analyse_pitch_range ~ parent_label , data = data)

summary(pitch_range_anova_parent)
```

```{r}
jitter_anova_parent <- aov(analyse_jitter ~ parent_label , data = data)

summary(jitter_anova_parent)
```

```{r}
shimmer_anova_parent <- aov(analyse_shimmer ~ parent_label , data = data)

summary(shimmer_anova_parent)
```

```{r}
spectral_slope_anova_parent <- aov(spectral_slope ~ parent_label , data = data)

summary(spectral_slope_anova_parent)
```

```{r}
spectral_rolloff_anova_parent <- aov(mean_spectral_rolloff ~ parent_label , data = data)

summary(spectral_rolloff_anova_parent)
```

## Segment Label Anova- All Data

```{r}
energy_anova_segment <- aov( get_energy ~ segment_label, data = data)

summary(energy_anova_segment)
```

```{r}
harmonics_anova_segment <- aov(analyse_harmonics ~ segment_label , data = data)

summary(harmonics_anova_segment)
```

```{r}
max_intensity_anova_segment <- aov(get_max_intensity ~ segment_label , data = data)

summary(max_intensity_anova_segment)
```
```{r}
intensity_anova_segment <- aov(analyse_intensity ~ segment_label , data = data)

summary(intensity_anova_segment)
```

```{r}
pitch_anova_segment <- aov(analyse_pitch ~ segment_label , data = data)

summary(pitch_anova_segment)
```


```{r}
pitch_range_anova_segment <- aov(analyse_pitch_range ~ segment_label , data = data)

summary(pitch_range_anova_segment)
```

```{r}
jitter_anova_segment <- aov(analyse_jitter ~ segment_label , data = data)

summary(jitter_anova_segment)
```

```{r}
shimmer_anova_segment <- aov(analyse_shimmer ~ segment_label , data = data)

summary(shimmer_anova_segment)
```

```{r}
spectral_slope_anova_segment <- aov(spectral_slope ~ segment_label , data = data)

summary(spectral_slope_anova_segment)
```

```{r}
spectral_rolloff_anova_segment <- aov(mean_spectral_rolloff ~ segment_label , data = data)

summary(spectral_rolloff_anova_segment)
```

## Post hoc Tukey Parent Label - All data

```{r}
energy_tukey_parent <- TukeyHSD( energy_anova_parent)

energy_tukey_parent

plot(energy_tukey_parent, las = 1)
```

```{r}
harmonics_tukey_parent <- TukeyHSD( harmonics_anova_parent)

harmonics_tukey_parent

plot(harmonics_tukey_parent, las = 1)
```

```{r}
max_intensity_tukey_parent <- TukeyHSD( max_intensity_anova_parent)

max_intensity_tukey_parent
plot(max_intensity_tukey_parent,las = 1)
```

```{r}
intensity_tukey_parent <- TukeyHSD( intensity_anova_parent)

intensity_tukey_parent
plot(intensity_tukey_parent, las = 1)
```

```{r}
pitch_tukey_parent <- TukeyHSD( pitch_anova_parent)

pitch_tukey_parent
plot(pitch_tukey_parent, las = 1)
```


```{r}
pitch_range_tukey_parent <- TukeyHSD( pitch_range_anova_parent)

pitch_range_tukey_parent
plot(pitch_range_tukey_parent, las = 1)
```

```{r}
jitter_tukey_parent <- TukeyHSD( jitter_anova_parent)

jitter_tukey_parent
plot(jitter_tukey_parent, las = 1)
```

```{r}
shimmer_tukey_parent <- TukeyHSD( shimmer_anova_parent)

shimmer_tukey_parent
plot(shimmer_tukey_parent, las = 1)
```

```{r}
spectral_slope_tukey_parent <- TukeyHSD( spectral_slope_anova_parent)

spectral_slope_tukey_parent
plot(spectral_slope_tukey_parent, las = 1)
```

```{r}
spectral_rolloff_tukey_parent <- TukeyHSD( spectral_rolloff_anova_parent)

spectral_rolloff_tukey_parent
plot(spectral_rolloff_tukey_parent, las = 1)
```

## Post hoc Tukey Segment Label - All data

```{r}
energy_tukey_segment <- TukeyHSD( energy_anova_segment)

energy_tukey_segment

plot(energy_tukey_segment, las = 1)
```

```{r}
harmonics_tukey_segment <- TukeyHSD( harmonics_anova_segment)

harmonics_tukey_segment

plot(harmonics_tukey_segment, las = 1)
```

```{r}
max_intensity_tukey_segment <- TukeyHSD( max_intensity_anova_segment)

max_intensity_tukey_segment
plot(max_intensity_tukey_segment,las = 1)
```

```{r}
intensity_tukey_segment <- TukeyHSD( intensity_anova_segment)

intensity_tukey_segment
plot(intensity_tukey_segment, las = 1)
```

```{r}
pitch_tukey_segment <- TukeyHSD( pitch_anova_segment)

pitch_tukey_segment
plot(pitch_tukey_segment, las = 1)
```


```{r}
pitch_range_tukey_segment <- TukeyHSD( pitch_range_anova_segment)

pitch_range_tukey_segment
plot(pitch_range_tukey_segment, las = 1)
```

```{r}
jitter_tukey_segment <- TukeyHSD( jitter_anova_segment)

jitter_tukey_segment
plot(jitter_tukey_segment, las = 1)
```

```{r}
shimmer_tukey_segment <- TukeyHSD( shimmer_anova_segment)

shimmer_tukey_segment
plot(shimmer_tukey_segment, las = 1)
```

```{r}
spectral_slope_tukey_segment <- TukeyHSD( spectral_slope_anova_segment)

spectral_slope_tukey_segment
plot(spectral_slope_tukey_segment, las = 1)
```

```{r}
spectral_rolloff_tukey_segment <- TukeyHSD( spectral_rolloff_anova_segment)

spectral_rolloff_tukey_segment
plot(spectral_rolloff_tukey_segment, las = 1)
```


We will only worry about segment labels to explore the differences between Noisy and non Noisy data, this is because we will be predicting based on segment labels, this is what a single feature related to, a parent label is simply the max of all it's segments


## Segment Label Anova- Non-Noisy Data

Get non noisy data

```{r}
non_noisy <- data[data$noisy==0,]
```

```{r}
energy_anova_segment_non_noisy <- aov( get_energy ~ segment_label, data = non_noisy)
energy_anova_segment_non_noisy <- data.frame(unclass(summary(energy_anova_segment_non_noisy)))[1,]
energy_anova_segment_non_noisy
```

```{r}
harmonics_anova_segment_non_noisy <- aov(analyse_harmonics ~ segment_label , data = non_noisy)
harmonics_anova_segment_non_noisy <-  data.frame(unclass(summary(harmonics_anova_segment_non_noisy)))[1,]
summary(harmonics_anova_segment_non_noisy)
```

```{r}
max_intensity_anova_segment_non_noisy <- aov(get_max_intensity ~ segment_label , data = non_noisy)
max_intensity_anova_segment_non_noisy <- data.frame(unclass(summary(max_intensity_anova_segment_non_noisy)))[1,]
summary(max_intensity_anova_segment_non_noisy)
```

```{r}
intensity_anova_segment_non_noisy <- aov(analyse_intensity ~ segment_label , data = non_noisy)
intensity_anova_segment_non_noisy <- data.frame(unclass(summary(intensity_anova_segment_non_noisy)))[1,]
summary(intensity_anova_segment_non_noisy)
```

```{r}
pitch_anova_segment_non_noisy <- aov(analyse_pitch ~ segment_label , data = non_noisy)
pitch_anova_segment_non_noisy <- data.frame(unclass(summary(pitch_anova_segment_non_noisy)))[1,]
summary(pitch_anova_segment_non_noisy)
```


```{r}
pitch_range_anova_segment_non_noisy <- aov(analyse_pitch_range ~ segment_label , data = non_noisy)
pitch_range_anova_segment_non_noisy <- data.frame(unclass(summary(pitch_range_anova_segment_non_noisy)))[1,]
summary(pitch_range_anova_segment_non_noisy)
```

```{r}
jitter_anova_segment_non_noisy <- aov(analyse_jitter ~ segment_label , data = non_noisy)
jitter_anova_segment_non_noisy <- data.frame(unclass(summary(jitter_anova_segment_non_noisy)))[1,]
summary(jitter_anova_segment_non_noisy)
```

```{r}
shimmer_anova_segment_non_noisy <- aov(analyse_shimmer ~ segment_label , data = non_noisy)
shimmer_anova_segment_non_noisy <- data.frame(unclass(summary(shimmer_anova_segment_non_noisy)))[1,]
summary(shimmer_anova_segment_non_noisy)
```

```{r}
spectral_slope_anova_segment_non_noisy <- aov(spectral_slope ~ segment_label , data = non_noisy)
spectral_slope_anova_segment_non_noisy <- data.frame(unclass(summary(spectral_slope_anova_segment_non_noisy)))[1,]
summary(spectral_slope_anova_segment_non_noisy)
```

```{r}
spectral_rolloff_anova_segment_non_noisy <- aov(mean_spectral_rolloff ~ segment_label , data = non_noisy)
spectral_rolloff_anova_segment_non_noisy <- data.frame(unclass(summary(spectral_rolloff_anova_segment_non_noisy)))[1,]
summary(spectral_rolloff_anova_segment_non_noisy)
```
```{r}
# Putting all into one dataframe/table
anova_results <- data.frame(rbind(energy_anova_segment_non_noisy, harmonics_anova_segment_non_noisy, max_intensity_anova_segment_non_noisy, intensity_anova_segment_non_noisy, pitch_anova_segment_non_noisy, pitch_range_anova_segment_non_noisy,jitter_anova_segment_non_noisy, shimmer_anova_segment_non_noisy, spectral_slope_anova_segment_non_noisy, spectral_rolloff_anova_segment_non_noisy))
anova_results$Pr..F. <- "< .001***"
row.names(anova_results) <- NULL
anova_results <- cbind(a = "", anova_results)
colnames(anova_results) <- c("", "Df", "Sum sq", "Mean sq", "F-Stat", "P-value")


# create HTML table using kableExtra
library(kableExtra)
anova_results %>% kable("html", digits=2) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  pack_rows(., "Energy",1,1) %>% # groups rows with label
  pack_rows(., "Harmonics", 2,2) %>% # groups rows with label
  pack_rows(., "Max Intensity", 3,3) %>% # groups rows with label
  pack_rows(., "Intensity", 4,4) %>% # groups rows with label
  pack_rows(., "Pitch", 5,5) %>% # groups rows with label
  pack_rows(., "Pitch Range",6,6) %>% # groups rows with label
  pack_rows(., "Jitter", 7,7) %>% # groups rows with label
  pack_rows(., "Shimmer", 8,8) %>% # groups rows with label
  pack_rows(., "Spectral Slope", 9,9) %>% # groups rows with label
  pack_rows(., "Spectral Rolloff", 10,10)
```

## Post hoc Tukey Segment Label - Non-Noisy

```{r}
energy_tukey_segment_non_noisy <- TukeyHSD( energy_anova_segment_non_noisy)

energy_tukey_segment_non_noisy

plot(energy_tukey_segment_non_noisy, las = 1)
```

```{r}
harmonics_tukey_segment_non_noisy <- TukeyHSD( harmonics_anova_segment_non_noisy)

harmonics_tukey_segment_non_noisy

plot(harmonics_tukey_segment_non_noisy, las = 1)
```

```{r}
max_intensity_tukey_segment_non_noisy <- TukeyHSD( max_intensity_anova_segment_non_noisy)

max_intensity_tukey_segment_non_noisy
plot(max_intensity_tukey_segment_non_noisy,las = 1)
```

```{r}
intensity_tukey_segment_non_noisy <- TukeyHSD( intensity_anova_segment_non_noisy)

intensity_tukey_segment_non_noisy
plot(intensity_tukey_segment_non_noisy, las = 1)
```

```{r}
pitch_tukey_segment_non_noisy <- TukeyHSD( pitch_anova_segment_non_noisy)

pitch_tukey_segment_non_noisy
plot(pitch_tukey_segment_non_noisy, las = 1)
```


```{r}
pitch_range_tukey_segment_non_noisy <- TukeyHSD( pitch_range_anova_segment_non_noisy)

pitch_range_tukey_segment_non_noisy
plot(pitch_range_tukey_segment_non_noisy, las = 1)
```

```{r}
jitter_tukey_segment_non_noisy <- TukeyHSD( jitter_anova_segment_non_noisy)

jitter_tukey_segment_non_noisy
plot(jitter_tukey_segment_non_noisy, las = 1)
```

```{r}
shimmer_tukey_segment_non_noisy <- TukeyHSD( shimmer_anova_segment_non_noisy)

shimmer_tukey_segment_non_noisy
plot(shimmer_tukey_segment_non_noisy, las = 1)
```

```{r}
spectral_slope_tukey_segment_non_noisy <- TukeyHSD( spectral_slope_anova_segment_non_noisy)

spectral_slope_tukey_segment_non_noisy
plot(spectral_slope_tukey_segment_non_noisy, las = 1)
```

```{r}
spectral_rolloff_tukey_segment_non_noisy <- TukeyHSD( spectral_rolloff_anova_segment_non_noisy)

spectral_rolloff_tukey_segment_non_noisy
plot(spectral_rolloff_tukey_segment_non_noisy, las = 1)
```

## Segment Label Anova- Noisy Data

Get noisy data

```{r}
noisy <- data[data$noisy==1,]
```

```{r}
energy_anova_segment_noisy <- aov( get_energy ~ segment_label, data = noisy)
energy_anova_segment_noisy <- data.frame(unclass(summary(energy_anova_segment_noisy)))[1,]
summary(energy_anova_segment_noisy)
```

```{r}
harmonics_anova_segment_noisy <- aov(analyse_harmonics ~ segment_label , data = noisy)
harmonics_anova_segment_noisy <- data.frame(unclass(summary(harmonics_anova_segment_noisy)))[1,]
summary(harmonics_anova_segment_noisy)
```

```{r}
max_intensity_anova_segment_noisy <- aov(get_max_intensity ~ segment_label , data = noisy)
max_intensity_anova_segment_noisy <- data.frame(unclass(summary(max_intensity_anova_segment_noisy)))[1,]
summary(max_intensity_anova_segment_noisy)
```

```{r}
intensity_anova_segment_noisy <- aov(analyse_intensity ~ segment_label , data = noisy)
intensity_anova_segment_noisy <- data.frame(unclass(summary(intensity_anova_segment_noisy)))[1,]
summary(intensity_anova_segment_noisy)
```

```{r}
pitch_anova_segment_noisy <- aov(analyse_pitch ~ segment_label , data = noisy)
pitch_anova_segment_noisy <- data.frame(unclass(summary(pitch_anova_segment_noisy)))[1,]
summary(pitch_anova_segment_noisy)
```


```{r}
pitch_range_anova_segment_noisy <- aov(analyse_pitch_range ~ segment_label , data = noisy)
pitch_range_anova_segment_noisy <- data.frame(unclass(summary(pitch_range_anova_segment_noisy)))[1,]
summary(pitch_range_anova_segment_noisy)
```

```{r}
jitter_anova_segment_noisy <- aov(analyse_jitter ~ segment_label , data = noisy)
jitter_anova_segment_noisy <- data.frame(unclass(summary(jitter_anova_segment_noisy)))[1,]
summary(jitter_anova_segment_noisy)
```

```{r}
shimmer_anova_segment_noisy <- aov(analyse_shimmer ~ segment_label , data = noisy)
shimmer_anova_segment_noisy <- data.frame(unclass(summary(shimmer_anova_segment_noisy)))[1,]
summary(shimmer_anova_segment_noisy)
```

```{r}
spectral_slope_anova_segment_noisy <- aov(spectral_slope ~ segment_label , data = noisy)
spectral_slope_anova_segment_noisy <- data.frame(unclass(summary(spectral_slope_anova_segment_noisy)))[1,]
summary(spectral_slope_anova_segment_noisy)
```

```{r}
spectral_rolloff_anova_segment_noisy <- aov(mean_spectral_rolloff ~ segment_label , data = noisy)
spectral_rolloff_anova_segment_noisy <- data.frame(unclass(summary(spectral_rolloff_anova_segment_noisy)))[1,]
summary(spectral_rolloff_anova_segment_noisy)
```

```{r}
# Putting all into one dataframe/table
anova_results <- data.frame(rbind(energy_anova_segment_noisy, harmonics_anova_segment_noisy, max_intensity_anova_segment_noisy, intensity_anova_segment_noisy, pitch_anova_segment_noisy, pitch_range_anova_segment_noisy,jitter_anova_segment_noisy, shimmer_anova_segment_noisy, spectral_slope_anova_segment_noisy, spectral_rolloff_anova_segment_noisy))
anova_results$Pr..F. <- c( ".16", "< .001***", ".97", ".28", "< .001***", "< .001***", "< .001***", ".01**", ".04*", "< .001***" )
row.names(anova_results) <- NULL
anova_results <- cbind(a = "", anova_results)
colnames(anova_results) <- c("", "Df", "Sum sq", "Mean sq", "F-Stat", "P-value")


# create HTML table using kableExtra
library(kableExtra)
anova_results %>% kable("html", digits=2) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  pack_rows(., "Energy",1,1) %>% # groups rows with label
  pack_rows(., "Harmonics", 2,2) %>% # groups rows with label
  pack_rows(., "Max Intensity", 3,3) %>% # groups rows with label
  pack_rows(., "Intensity", 4,4) %>% # groups rows with label
  pack_rows(., "Pitch", 5,5) %>% # groups rows with label
  pack_rows(., "Pitch Range",6,6) %>% # groups rows with label
  pack_rows(., "Jitter", 7,7) %>% # groups rows with label
  pack_rows(., "Shimmer", 8,8) %>% # groups rows with label
  pack_rows(., "Spectral Slope", 9,9) %>% # groups rows with label
  pack_rows(., "Spectral Rolloff", 10,10)
```
## Post hoc Tukey Segment Label - Noisy data


```{r}
harmonics_tukey_segment_noisy <- TukeyHSD( harmonics_anova_segment_noisy)

harmonics_tukey_segment_noisy

plot(harmonics_tukey_segment_noisy, las = 1)
```

```{r}
pitch_tukey_segment_noisy <- TukeyHSD( pitch_anova_segment_noisy)

pitch_tukey_segment_noisy
plot(pitch_tukey_segment_noisy, las = 1)
```


```{r}
pitch_range_tukey_segment_noisy <- TukeyHSD( pitch_range_anova_segment_noisy)

pitch_range_tukey_segment_noisy
plot(pitch_range_tukey_segment_noisy, las = 1)
```

```{r}
jitter_tukey_segment_noisy <- TukeyHSD( jitter_anova_segment_noisy)

jitter_tukey_segment_noisy
plot(jitter_tukey_segment_noisy, las = 1)
```

```{r}
shimmer_tukey_segment_noisy <- TukeyHSD( shimmer_anova_segment_noisy)

shimmer_tukey_segment_noisy
plot(shimmer_tukey_segment_noisy, las = 1)
```

```{r}
spectral_slope_tukey_segment_noisy <- TukeyHSD( spectral_slope_anova_segment_noisy)

spectral_slope_tukey_segment_noisy
plot(spectral_slope_tukey_segment_noisy, las = 1)
```

```{r}
spectral_rolloff_tukey_segment_noisy <- TukeyHSD( spectral_rolloff_anova_segment_noisy)

spectral_rolloff_tukey_segment_noisy
plot(spectral_rolloff_tukey_segment_noisy, las = 1)
```
